On investigating heterogeneity in psychological phenomena

### 2024-03-21 ms.Rmd
Comment Grice et al. (2020)

In the current work, we illustrated the use of practical descriptors of heterogeneity in psychological phenomena with examples drawn from social and cognitive psychology. Our aim was to incrementally build on the work of @bolgerCausalProcessesPsychology2019 and others---who have described the importance and available methods for examining heterogeneity in causal effects in psychology---by describing how it is both critically important and practically feasible to incorporate uncertainty in analyses and descriptions of heterogeneity. We believe our currently proposed methods to be particularly useful to researchers because they allow doing just that: Incorporating uncertainty in the analyses at every stage, from modelling to communicating resulting inferences.

>>>>

In the current work, we illustrated the use of practical descriptors of heterogeneity in psychological phenomena with examples drawn from social and cognitive psychology. Our aim was to incrementally build on the work of @bolgerCausalProcessesPsychology2019 and others---who have described the importance and available methods for examining heterogeneity in causal effects in psychology---by describing how it is both critically important and practically feasible to incorporate uncertainty in analyses and descriptions of heterogeneity.

Although prior work on developing metrics of heterogeneity, and placing experimental effect sizes in context of person-specific effects exists, it mostly has ignored estimation uncertainty and thus remained purely descriptive. For example, @gricePersonsEffectSizes2020 describe a method whereby analysts simply count the number of individuals whose point estimate of an effect is concordant with a hypothesis. But such counting ignores estimation uncertainty in both the person-specific effects and variability among them. By accounting for these uncertainties, the methods described here go beyond description and allow inference to be drawn regarding populations and individuals with confidence.
